Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Draft Decompostion section
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@5 db7c848b-7755-4df2-b763-8796797afa52

\usepackage{color}
\definecolor{RED}{rgb}{1,0,0}
\definecolor{BLUE}{rgb}{0,0,1}
\newcommand{\FIXME}[1]{\textbf{\color{BLUE}{FIXME: #1}}}
%\newcommand{\FIXME}[1]{}

@@

Interaction with threading

@@

Equalizers do what?

@@

Equal load for fill-limited apps

@@

MSAA and DOF, plus idle refinement algo

@@

\subsubsection{Thread Synchronization Modes}

>>>>

\usepackage{color}
\definecolor{RED}{rgb}{1,0,0}
\definecolor{BLUE}{rgb}{0,0,1}
\newcommand{\FIXME}[1]{\textbf{\color{BLUE}{FIXME: #1}}}
\newcommand{\sref}[1]{Section~\ref{#1}}
%\newcommand{\FIXME}[1]{}

@@

Time-multiplexing, or DPlex, was already implemented in \cite{BRE:05}. While it
increases the framerate linearly, it does not decrease the latency between user
input and the corresponding output. Consequently, this decomposition mode is
mostly useful for non-interactive movie generation. It is transparent to
Equalizer applications, but does require the configuration latency to be equal
or greater than the number of source channels. Furthermore, to work in a
multi-threaded, multi-GPU configuration, the application needs to support
running the rendering threads asynchronously, as outlined in
\sref{SEC_threading}.

@@

Tile and chunk decompositions are a variant of sort-first and sort-last
rendering, respectively. They decompose the scene into a predefined set of
fixed-size image tiles or database ranges. These tasks are queued and processed
by all source channels by polling a server-central queue. Prefetching ensures
that the task communication overlaps with rendering. As shown in \cite{SPEP:16},
these modes provide better performance due to being inherently load-balanced, as
long as there is an insignificant overhead for the render task setup. This mode
is transparent to Equalizer applications.

@@

Pixel compounds decompose the destination channel by interleaving rows or
columns in image space. They are a variant of sort-first decomposition which
works well for fill-limited applications which are not geometry bound. Source
channels cannot reduce geometry load through view frustum culling, since each
source channel has almost the same frustum (only shifted by some pixels),
but applied to a reduced 2D viewport. However, the fragment load on all source
channels is very similar due to the interleaved distribution of pixels. This
functionality is transparent to Equalizer applications, and the default
compositing implementation uses the OpenGL stencil buffer to blit pixels onto
the destination channel.

@@

Subpixel compounds are similar to pixel compounds, but they decompose the work
for a single pixel, for example when using multisampling or depth of
field. Composition typically uses accumulation and averaging of all computed
fragments for a pixel. This feature is not fully transparent to the application,
since it needs to adapt (jitter or tilt) the frustum based on the iteration
executed. Furthermore, subpixel compounds interact with idle image refinements,
e.g., they can accelerate idle anti-aliasing of a scene when the camera and
scene are not changed.

@@

\subsubsection{Thread Synchronization Modes}\label{SEC_threading}
